Ecosystem size and complexity are extrinsic drivers of food chain length in branching networks

### 2022-05-10 rmd/manuscript.Rmd
edit: misc

where $m_{down}$ and $m_{up}$ are the disturbance values at down- and upstream patches, and the local environmental noise at the downstream patch $\epsilon$ was drawn from $Normal(0, \sigma_{l}^2)$. This autoregressive process resembles a natural disturbance regime, where flood or drought disturbance cascades downstream with some local variation along the channel [@nakamuraDisturbanceRegimesStream2000]. At confluence patches, the disturbance value takes a weighted mean based on the relative size of the two contributing branches, $Q$ (the number of upstream contributing patches):

@@

$m_{1,up}$ and $m_{2,up}$ are the disturbance values of upstream contributing tributaries, $\epsilon_1$ and $\epsilon_2$ are independent local noises, and $\omega$ the relative size of one tributary over another defined as $\omega = \frac{Q_{1}}{Q_{1} + Q_{2}}$. Thus, the larger tributary has a greater influence on the downstream environment, as observed in natural river networks [@bendaNetworkDynamicsHypothesis2004]. Disturbance value distributions had medians close to $m$ with long tails (**Figure 1B**). The low-magnitude patches can be viewed as refugia, which supply individuals to impacted sites in subsequent time steps.

@@

$$
K_{x} = K_{base}(N_{p,up} + 1)^z
$$

where $K_{base}$ is the carrying capacity at the upstream terminal patch, $N_{p,up}$ the number of patches upstream, and $z$ the scaling exponent. We used $K_{base} = 100$ and $z = 0.54$ based on an empirical relationship of gross primary production and watershed area [@finlayStreamSizeHuman2011].

>>>>

where $m_{down}$ and $m_{up}$ are the disturbance values at down- and upstream patches, and the local environmental noise at the downstream patch $\epsilon$ was drawn from $Normal(0, \sigma_{l}^2)$. This autoregressive process resembles a natural disturbance regime, where flood or drought disturbance cascades downstream with some local variation along the channel [@nakamuraDisturbanceRegimesStream2000]. At confluence patches, the disturbance value takes a weighted mean based on the relative size of the two contributing branches, $Q$ (the number of upstream contributing patches + 1):

@@

$m_{1,up}$ and $m_{2,up}$ are the disturbance values of upstream contributing tributaries, $\epsilon_1$ and $\epsilon_2$ are independent local noises, and $\omega$ the relative size of one tributary over another defined as $\omega = \frac{Q_{1}}{Q_{1} + Q_{2}}$. Thus, the larger tributary has a greater influence on the downstream environment, as observed in natural river networks [@bendaNetworkDynamicsHypothesis2004]. Disturbance value distributions had medians close to $\mu_m$ with long tails (**Figure 1B**). The low-magnitude patches can be viewed as refugia, which supply individuals to impacted sites in subsequent time steps.

@@

$$
K_{x} = K_{base}Q_{x}^z
$$

where $K_{base}$ is the carrying capacity at the upstream terminal patch, and $z$ the scaling exponent. In this formulation, the most upstream patch, at which $Q_x = 1$ (the number of upstream patches + 1), has the carrying capacity of $K_{base}$. We used $K_{base} = 100$ and $z = 0.54$ based on an empirical relationship of gross primary production and watershed area [@finlayStreamSizeHuman2011].

### 2022-05-10 rmd/suppl_info.Rmd
edit: misc

# Sensitivity data
source(here::here("code/analysis_stvy.R"))
load(file = here::here("output/result_stvy.RData"))

@@

Based on the results, we considered ecological scenarios relevant for putative controls of food chain: low and high productivity ($r_b = 4, 8$), low and high disturbance ($p_m = 0.01, 0.1$), and three food web architecture ("Chain" [$\{e_{BC}, e_{BP}, e_{CP}\} = \{4, 0, 4\}, \{a_{BC}, a_{BP}, a_{CP}\} = \{0.5, 0.1, 0.5\}$], "Weak omnivory" [$\{e_{BC}, e_{BP}, e_{CP}\} = \{4, 2, 4\}, \{a_{BC}, a_{BP}, a_{CP}\} = \{0.5, 0.1, 0.5\}$], and "Strong omnivory" [$\{e_{BC}, e_{BP}, e_{CP}\} = \{4, 4, 2\}, \{a_{BC}, a_{BP}, a_{CP}\} = \{0.5, 0.5, 0.1\}$]). Handling times were fixed at $0.5$ to reduce the number of parameter combinations.

>>>>

# Sensitivity data
source(here::here("code/analysis_stvy.R"))
load(file = here::here("output/result_main.RData"))
load(file = here::here("output/result_stvy.RData"))

@@

Based on the results, we considered ecological scenarios relevant for putative controls of food chain: low and high productivity ($r_b = 4, 8$), and low and high disturbance ($p_m = 0.01, 0.1$). We also investigated the role of omnivory by changing attack rate ($a_{BP}$ and $a_{CP}$) and conversion efficiency ($e_{BP}$ and $e_{CP}$) of two prey items for predator $P$. Specifically, we used the following combinations to represent three levels of omnivory: "Chain", $\{a_{BP}, a_{CP}, e_{BP}, e_{CP}\}=\{$ `r c(min(sim_main_result$a_bp), max(sim_main_result$a_cp), unique(sim_main_result$e_bp)[1], max(sim_main_result$e_cp))` $\}$; "Weak omnivory", $\{a_{BP}, a_{CP}, e_{BP}, e_{CP}\}=\{$ `r c(min(sim_main_result$a_bp), max(sim_main_result$a_cp), unique(sim_main_result$e_bp)[2], max(sim_main_result$e_cp))` $\}$; and "Strong omnivory", $\{a_{BP}, a_{CP}, e_{BP}, e_{CP}\}=\{$ `r c(max(sim_main_result$a_bp), min(sim_main_result$a_cp), unique(sim_main_result$e_bp)[3], min(sim_main_result$e_cp))` $\}$. To simplify simulation setup, we fixed the following parameters: $e_{BC}=$ `r unique(sim_main_result$e_bc)` , $a_{BC}=$ `r unique(sim_main_result$a_bc)`, and $h_{ij}=$ `r unique(sim_main_result$h_bc)`.
